Automated Synthesis of State-Space Digital Systems

### 2016-12-07 cav2017/cav2017.tex
Benchmarks
figure fix

\textcolor{red}{LC: Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.9cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    (verif1) edge node {Generalise} (verif2)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=5em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
    ([xshift=-5em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=6.5cm]aux2)
   ([xshift=6.5cm]aux2) edge node[align=center] {Increase parameters} (aux1);

\end{tikzpicture}
\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}. \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}}
\end{figure}

@@

The third benchmark is an ball magnetic levitation model extracted from~\cite{maglev}. It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
0		& 1 		& 0		\\
1752	& 0			& -34.07\\
0		& 0			& -38.27\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0 \\ 0 \\ 1.923
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
z \\ \dot{z} \\ i \\
\end{array}\right],
$$
where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.

>>>>

\textcolor{red}{LC: Cristina, may I ask you to expand further this section by connecting it to our control-synthesis work?}
\begin{figure}
\centering
\hspace*{-1cm}
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=1.5cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \node[fill=yellow!20,align=center] (synth) {{\sc inductive}\\{\sc generalisation}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dashed,
	minimum width=6.7cm,
	minimum height=.8cm,
	label={\sc Validation oracles},] (verif) {};
   \node[fill=yellow!20] (verif1) at ([xshift=-2.1cm]verif.center) {{\sc Validate}};
   \node[fill=yellow!20,align=center] (verif2) at ([xshift=1.7cm]verif.center) {{\sc validate general}};
   } 
   \& \node[ellipse, fill=yellow!20] (done) {{\sc Done}};\\
   %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
   %% \&
   %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
   \& \\
   \& \\
   \node (gp) {Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.1cm]aux.center) {SAT/SMT Solver};
   \node (fp)  at ([xshift=1.9cm]aux.center) {SAT/SMT Solver};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.7em] {Candidate} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node[xshift=-0.7em] {New input} ([yshift=-2em]synth.east)
    (verif1) edge node {Generalise} (verif2)
    ([xshift=5em]verif1.south) edge node[align=center] {Candidate} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {Candidate} ([xshift=3.8em]fp.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif1.south)
    ([xshift=-6.2em]fp.north) edge node[align=center]  {UNSAT/\\Model} ([xshift=-5em]verif2.south)
    (verif2) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {{\sc Inputs}} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {No solution/\\Candidate} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=5.6cm]aux2)
   ([xshift=5.6cm]aux2) edge node[align=center] {Increase parameters} (aux1);

\end{tikzpicture}
\caption{The CEGIS loop with solution generalisation\label{fig:CEGIS-multiple-verif}.}
\end{figure}

  %% \textcolor{red}{LC: Cristina, can you please fix this figure? The text ``candidate'' overlaps with the dotted box.}

@@

The third benchmark is a ball magnetic levitation model extracted from~\cite{maglev}. It is a third order system presents the following set of matrices $\textbf{A}$, $\textbf{B}$, $\textbf{C}$, $\textbf{D}$, and $\textbf{x}$:
$$
\textbf{A}=\left[\begin{array}{ccc}
0		& 1 		& 0		\\
1752	& 0			& -34.07\\
0		& 0			& -38.27\\
\end{array}\right],~~ \textbf{B} = \left[\begin{array}{c}
0 \\ 0 \\ 1.923
\end{array}\right]
$$
%
$$
\textbf{C}=\left[\begin{array}{ccc}
1 & 0 & 0\\
\end{array}\right],~~ \textbf{D}= 0,~~ \textbf{x}=\left[\begin{array}{c}
z \\ \dot{z} \\ i \\
\end{array}\right],
$$
where the states $z$, $\dot{z}$, and $i$ are respectively the vertical displacement of the ball, its rate and the coil current. This system  is unstable in open loop.
